---
title: "Tidy Tuesday Appa"
tags: 
- R
- Tidy Tuesday
categories:
- R
- Tidy Tuesday
output: 
  html_notebook:
    theme: cosmo
  blogdown::html_page:
      toc: true
      fig_width: 6
      dev: "svg"
---


## Load data and packages
```{r message=TRUE, warning=FALSE}
library(tibble)
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)

library(igraph)
library(tidygraph)
library(ggplot2)
library(ggraph)

avatar <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-11/avatar.csv')
scene_description <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-11/scene_description.csv')
```

Let's make a simple graph to see the connection among characters and some important concepts in the series. The most times the character said something, stronger will be the connection between them. This will show in proximity and size of the connection in the network.

```{r}
# Get rid of scene descriptions
avatar <- avatar %>% 
          filter(character != "Scene Description")
```
## Select characters and words of interest
Also classify each one as pertaining to one of the tribes or
a concept.
```{r}
characters <- c("Aang", "Sokka", "Katara", "Toph", "Zuko",
                 "Iroh", "Ozai","Azula")
words_of_interest <- c("Avatar", "Aang", "Sokka", "Katara", 
                       "Toph", "Zuko", "Iroh", "Fire Lord",
                       "Azula", "kill", "Sozin's Comet", 
                       "save", "Earth Kingdom", "spirit",
                       "Appa","bison" ,"Ozai", "moon",
                       "Agni Kai", "bending", "water tribe",
                       "balance", "honor", "Dai Li")

tribes <- c("concept", "air", "water","water",
            "earth", "fire", "fire", "fire",
            "fire", "concept","fire",
            "concept", "earth", "concept",
            "air", "air", "fire", "water",
            "fire", "concept", "water",
            "concept", "concept", "earth")

levels_tribes <- sort(unique(tribes))
tribes <- data.frame(words = words_of_interest, 
                     tribes = factor(tribes,
                                     levels = levels_tribes,
                                     ordered = TRUE
                                     )
                     )
```

## Prepare graph
```{r}
adjacencies <- rep(list(words_of_interest),length(characters))
names(adjacencies) <- characters

adjacencies <- adjacencies %>% 
  enframe("character", "word") %>% 
  unnest(word) %>% 
   nest_join(select(avatar,character, character_words),
             "character", name = "lines") %>% 
  group_by(character, word) %>% 
  mutate(weight = map_dbl(lines, ~sum(str_count(.$character_words, word)))) %>% 
  filter(weight > 4, character != word) %>% 
  select(-lines)

graph <- graph_from_data_frame(adjacencies)
graph <- as_tbl_graph(graph)
graph <- left_join(graph, tribes, by = c(name = "words"))
```


```{r}
theme_set(theme_bw(16))

# Avatar fill color scale
avatar_fill <- function (...) { scale_fill_manual(values =  c(
                               "#F1B84A", "grey20", 
                               "#4FA24C", "#900B0B",
                               "#4A82CB")
) }
avatar_color <- function (...) { scale_colour_manual(values =  c(
                               "#F1B84A", "grey20", 
                               "#4FA24C", "#900B0B",
                               "#4A82CB")
) }
# Avatar font
windowsFonts(avatar_font = windowsFont("Herculanum"))

ggraph(graph, layout = 'fr')+
    geom_edge_link(aes(width = weight), color = 'grey70')+
    geom_node_point(aes(color = tribes))+
    geom_node_label(aes(label = name, fill = tribes),
                    color = "white", fontface = "bold",
                    family = "avatar_font", size = 6,
                    repel = TRUE)+
   avatar_fill()+
  avatar_color()+
  theme(legend.position = "top")+
  labs(title = "Avatar referencing graph", color = "Tribes",
       fill = "Tribes", width = "Weight")

# Not embedding fonts for some reason... =/
#ggsave('avatar_graph.png', type = "cairo", dpi = 400)
```

